Verifying Demonstrations

### 2020-06-03 paper/performance.tex
Improves performance table

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.

@@

The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
performs one signature verification and four additional proofs in parallel.
The cost for the verifier is one signature verification in addition to the 
factor \(m\) of randomness used.
On the prover side, we have the computations for the signature verification and 
four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).

The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
implements a public transport pass using this signature scheme.
The signature need not be reverified \(n\) times, it is sufficient to verify 
that once and reuse the same blinding for all \(n\) repetitions of the 
protocol.
Thus it is only the \acl{PK} that must be rerun \(n\) times.

>>>>

\mode<presentation>{%
  \begin{frame}
    \begin{question}
      \begin{itemize}
        \item How costly is this compared to non-\acs{DB} Schnorr?
      \end{itemize}
    \end{question}
  \end{frame}
}

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.
We summarize the results in \cref{performance-overview}.

\begin{frame}
  \begin{table}
    \centering
    \caption{%
      A summary of how costly \acl*{DB} is in terms of randomness, arithmetic 
      operations (addition, multiplication), exponentiations and pairing 
      operations.
      \(m, l\in \mathcal{O}(\log \lambda)\) and we must repeat the protocol 
      \(n\) times to achieve desired soundness.
    }\label{performance-overview}
    \begin{tabular}{lrrrr}
      \toprule
      Protocol
      & Rand.~(\si{\bit})
      & Arith.~(\(+, \times\))
      & Exp.
      & Pairings\\
      \midrule
      Schnorr             & \((\lambda+l)n\)  & \(3n\) & \(3n\) & 0\\
      DB, mutual          & \((\lambda+ml)n\) & \(3mn\)& \(3n\) & 0\\
      DB, \acs*{PKI} \(\sum\)
                          & \(4\lambda + (5\lambda + ml)n\)
                          & \((10m+8)n\)
                          & \(9 + 16n\)
                          & \(14\)\\
      ---\acs*{DHKE}      & \(2\lambda\)      & 0    & 4      & 0\\
      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
      ---DB               & \(5\lambda + ml\) & \(10m + 2\) & 6 & 0\\
      ---Verification     & 0    & 6 & 10 & 6\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
performs one signature verification and four additional proofs in parallel.
The cost for the verifier is one signature verification 
(CL04~\cite{CLsignatures}) in addition to the factor \(m\) of randomness used.
On the prover side, we have the computations for the signature verification and 
four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).

The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
implements a public transport pass using this signature scheme.
This signature verification introduces more additions, multiplications, 
exponentiations and pairing operations.
However, the signature will only be blinded and verified once, so this 
represents a constant factor.
It is sufficient to verify it once and reuse the same blinding for all \(n\) 
repetitions of the protocol.
(The same is true for the \ac{DHKE}.)
Thus it is only the \acl{PK} that must be rerun \(n\) times.
